\documentclass[a4paper]{article}

\begin{document}

    \subsection*{Abstract} % (fold)
    \label{sub:abstract}
            The purpose of this project is to find an alternative and more 
            user friendly way of installing and controlling a sun panel 
            manufactured by Parans Solar Lighting. As of today the panel is 
            installed and controlled by connecting it to a computer, 
            which has to be correctly configured and able to run a terminal 
            where commands are sent to the panel. The aim of this project is 
            to develop a hand held device which is easy to connect and has 
            buttons that execute the commands needed to install and control 
            the panel. The resulting device is a Raspberry Pi with an attached
            touchscreen, running a software developed in \texttt{Python}.  
            The conclusion is that such a device is easily created with standard
            hardware, although this results in a large device 
            compared to other touchscreen devices such as smartphones.
            
    % subsection abstract (end)
    \subsection*{Sammandrag} % (fold)
    \label{sub:sammandrag}
            Detta projekt ämnar hitta ett mer användarvänligt sätt att
            installera och styra en solpanel från Parans Solar Lighting. Idag
            utförs detta genom att ansluta panelen till en dator som måste vara
            korrekt konfigurerad och kunna köra ett terminalprogram för att
            skicka instruktioner till panelen. Målsättningen är att utveckla en
            handhållen enhet som är enkel att ansluta och har knappar som
            skickar instruktioner till panelen. Den enhet som tagits fram är en
            Raspberry Pi med pekskärm som kör mjukvara utvecklad i
            \texttt{Python}. Slutsatsen är att en sådan enhet med lätthet kan
            framställas med hjälp av existerande hårdvara. Detta resulterar dock
            i en större enhet jämfört med andra pekskärmsenheter såsom
            smarttelefoner.

    % subsection sammandrag (end)
\end{document}
